A Flexible Generator of Constrained Global Optimization Test Problems

### 2018-04-30 2018/LeGo/LeGo.tex
Исправил non- convex на non-convex, дважды :)

In the present paper, the methods for generating the global optimization test problems with non-
convex constraints
\begin{eqnarray}
&\varphi(y^\ast)=\min{\left\{\varphi(y):y\in D, \; g_i(y)\leq 0, \; 1 \leq i \leq m\right\}}, 
\label{i_problem} \\
&D=\left\{y\in R^N: a_i\leq y_i \leq b_i, 1\leq i \leq N\right\} \label{D}
\end{eqnarray}
are considered. The objective function $\varphi(y)$ (henceforth denoted by $g_{m+1}(y)$) and 
the left-hand sides $g_i(y), \; 1\leq i \leq m,$ of the constraints are supposed to satisfy the 
Lipschitz condition
\[ \left|g_i(y')-g_i (y'')\right| \leq L_i \left\|y'-y'' \right\|, \; y',y''\in D, \; 1\leq i \leq m+1. \]
with the Lipschitz constants unknown a priori. The analytical formulae of the problem functions 
may be unknown, i.e. these ones may be defined by an algorithm for computing the function 
values in the search domain (so called ``black-box''-functions). It is supposed that even a single 
computing of a problem function value may be a time-consuming operation since it is related to 
the necessity of numerical modeling in the applied problems (see, for example, 
\cite{Menniti2008,Kvasov2015,Modorskii2017}).

@@

This paper considers the method for generating the global optimization test problems with non-
convex constraints, which allows:
\begin{itemize}
	\item controlling the size of the feasible domain with respect to the whole domain of the 
parameters' variation;
	\item knowing a priori the conditional global minimizer of the objective 
function;
	\item generating the unconditional global minimizer of the objective function out of the 
feasible domain;
	\item generating the problems with a conditional minimizer located at the boundary 
of the feasible domain;
	\item defining the number of constraints active at the optimum point.
\end{itemize}

>>>>

In the present paper, the methods for generating the global optimization test problems with non-convex constraints
\begin{eqnarray}
&\varphi(y^\ast)=\min{\left\{\varphi(y):y\in D, \; g_i(y)\leq 0, \; 1 \leq i \leq m\right\}}, 
\label{i_problem} \\
&D=\left\{y\in R^N: a_i\leq y_i \leq b_i, 1\leq i \leq N\right\} \label{D}
\end{eqnarray}
are considered. The objective function $\varphi(y)$ (henceforth denoted by $g_{m+1}(y)$) and 
the left-hand sides $g_i(y), \; 1\leq i \leq m,$ of the constraints are supposed to satisfy the 
Lipschitz condition
\[ \left|g_i(y')-g_i (y'')\right| \leq L_i \left\|y'-y'' \right\|, \; y',y''\in D, \; 1\leq i \leq m+1. \]
with the Lipschitz constants unknown a priori. The analytical formulae of the problem functions 
may be unknown, i.e. these ones may be defined by an algorithm for computing the function 
values in the search domain (so called ``black-box''-functions). It is supposed that even a single 
computing of a problem function value may be a time-consuming operation since it is related to 
the necessity of numerical modeling in the applied problems (see, for example, 
\cite{Menniti2008,Kvasov2015,Modorskii2017}).

@@

This paper considers the method for generating the global optimization test problems with non-convex constraints, which allows:
\begin{itemize}
	\item controlling the size of the feasible domain with respect to the whole domain of the 
parameters' variation;
	\item knowing a priori the conditional global minimizer of the objective 
function;
	\item generating the unconditional global minimizer of the objective function out of the 
feasible domain;
	\item generating the problems with a conditional minimizer located at the boundary 
of the feasible domain;
	\item defining the number of constraints active at the optimum point.
\end{itemize}
